# NOTE:
# The public dataset supplied with this portfolio is synthetic and is
# intended to demonstrate the analysis workflow only. It does not reproduce
# the statistical findings of the original study.

#注意：作品集内使用的数据是虚拟数据，仅用于展示代码流程。不代表原始统计结果



```{r setup, include=FALSE}
library("knitr")
knitr::opts_chunk$set(
  echo = TRUE, 
  eval = TRUE, 
  warning = FALSE,   
  message = FALSE, 
  error = TRUE)
```

```{r install, include=FALSE}
library("pacman")
packages <- c("tidyverse","ggplot2", 
              "ggpubr","pwr","lme4","lmerTest","emmeans","DHARMa")
p_load(packages, character.only=TRUE) 
```

#1. Data import and validation（数据导入和验证）

#load the file(加载文件)
```{r read, include=FALSE}
library(here)

df_all <- read_csv(
  here("sample data",  "df_pass_sample.csv"))

df_7v7 <- filter(df_all, Format == "7v7")#只提取部分数据
df_11v11 <- filter(df_all, Format == "11v11")#只提取部分数据

```

# Basic validation of imported analysis data(简单检查导入的数据)
```{r read, include=True}
dim(df_all)
names(df_all)

colSums(is.na(
  df_all[c(
    "xT_added",
    "start_zone",
    "end_zone",
    "score_state",
    "Format",
    "Condition")]))
```
#2.Outcome A:xT_added

#2.1 Candidate models（建立候选模型）

#Establish two candidate models, 
#Model 1 is an additive model without an interaction term, 
#Model 2 includes an interaction between Condition and Transition.
#（建立两个模型候选模型，模型1为不包含交互项的加性模型，模型2包含 Condition 与 Transition 的交互效应。）
```{r xT_added, include=TRUE}

#11v11 game format:
LM_11v11_1 <- lmer(xT_added ~ Condition+ Transition + score_state +(1 | match_id),
           data = df_11v11)

LM_11v11_2 <- lmer(xT_added ~ score_state+ Condition*Transition +(1 | match_id),
             data = df_11v11)


#7v7 game format:
LM_7v7_1 <- lmer(xT_added ~ Condition+ Transition + score_state +(1 | match_id),
             data = df_7v7)

LM_7v7_2 <- lmer(xT_added ~ score_state+ Condition*Transition +(1 | match_id),
               data = df_7v7)

```



#2.2 Model selection（模型选择）
# Compare nested candidate models using likelihood-ratio tests and AIC.
# The interaction model was retained only when it provided clear evidence
# of improved model fit; otherwise, the simpler additive model was preferred.
# 使用似然比检验和 AIC 比较嵌套候选模型。
# 仅当交互模型能够明显改善模型拟合时保留交互项；
# 否则优先选择更简约的加性模型。
```{r xT_added, include=TRUE}
anova(LM_11v11_1, LM_11v11_2)

anova(LM_7v7_1, LM_7v7_2)
```


# 2.3. Model diagnostics(模型诊断)

#11v11:
```{r xT_added, include=TRUE}
plot(LM_11v11_1)                  # residuals vs fitted
qqnorm(resid(LM_11v11_1))
qqline(resid(LM_11v11_1))
hist(resid(LM_11v11_1))
```
#7v7:
```{r xT_added, include=TRUE}
plot(LM_7v7_1)                  # residuals vs fitted
qqnorm(resid(LM_7v7_1))
qqline(resid(LM_7v7_1))
hist(resid(LM_7v7_1))
```
   


#2.4 Statistical inference（统计推断）

#check the summary of retained model
```{r xT_added, include=TRUE}
summary(LM_11v11_1)

summary(LM_7v7_1)
```
#Model inference 
```{r xT_added, include=TRUE}
drop1(LM_11v11_1,test = "Chisq") 
```
```{r xT_added, include=TRUE}
drop1(LM_7v7_1,test = "Chisq") 
```
## Post-hoc analysis of interaction effects(交互效应的事后分析)

# In the original study, post-hoc pairwise comparisons were performed
# where the retained model included a Condition × Transition interaction.
# Synthetic demonstration data selected a different candidate model;
# therefore, the code below demonstrates the original follow-up procedure.
#原始研究中保留了一项包含Condition × Transition交互的模型，并进行了相应的事后分析，
#尽管合成演示数据选择了不同的候选模型。以下代码展示了原始的后续分析流程。
```{r xT_added, include=TRUE}
contrast_7v7<- emmeans(
  LM_7v7_2, ~ Condition | Transition)%>%
  pairs(adjust = "tukey")  

summary(contrast_7v7, infer = c(TRUE, TRUE))
```

# 2.5. Sensitivity analysis (敏感性分析)
#To assess the influence of extreme xT-added values, 
#a sign-preserving logarithmic transformation was applied:
#为评估极端 xT-added 值对结果的影响，对 xT-added 进行保留符号的对数变换。

#x′=sign(x)log(1+∣x∣). 

```{r Sensitivity1, include=TRUE}
#11v11:
df_11v11$log_xt <- sign(df_11v11$xT_added) *
              log1p(abs(df_11v11$xT_added))

LM_log_11v11 <- lmer(
  log_xt ~ Condition + Transition + score_state + (1|match_id),
  data = df_11v11)

drop1(LM_log_11v11,test = "Chisq")
```
```{r Sensitivity1, include=TRUE}
#7v7:
df_7v7$log_xt <- sign(df_7v7$xT_added) *
              log1p(abs(df_7v7$xT_added))

LM_log_7v7 <- lmer(
  log_xt ~ Condition + Transition + score_state + (1|match_id),
  data = df_7v7)

drop1(LM_log_7v7,test = "Chisq")
```

   

  
#3. Outcome B: Positive xT

# 3.1 Candidate models（建立候选模型）

##Establish two candidate models, 
#Model 1 is an additive model without an interaction term, 
#Model 2 includes an interaction between Condition and Transition.
#（建立两个模型候选模型，模型1为不包含交互项的加性模型，模型2包含 Condition 与 Transition 的交互效应。）
```{r positive, include=TRUE}
#11v11:
GLM_11v11_1 <- glmer(
  positive_xt ~ Condition + Transition + score_state + (1 | match_id),
  data = df_11v11, family = binomial)

GLM_11v11_2 <- glmer(
  positive_xt ~ score_state+ Condition*Transition + (1 | match_id),
  data = df_11v11, family = binomial)

#7v7:
GLM_7v7_1 <- glmer(
  positive_xt ~ Condition + Transition + score_state + (1 | match_id),
  data = df_7v7, family = binomial)

GLM_7v7_2 <- glmer(
  positive_xt ~ score_state+ Condition*Transition + (1 | match_id),
  data = df_7v7, family = binomial)
```

##3.2 Model selection（模型选择）
# Compare nested candidate models using likelihood-ratio tests and AIC.
# The interaction model was retained only when it provided clear evidence
# of improved model fit; otherwise, the simpler additive model was preferred.
# 使用似然比检验和 AIC 比较嵌套候选模型。
# 仅当交互模型能够明显改善模型拟合时保留交互项；
# 否则优先选择更简约的加性模型。
```{r positive, include=TRUE}
anova(GLM_11v11_1, GLM_11v11_2)

anova(GLM_7v7_1, GLM_7v7_2)
```

# 3.3. Model diagnostics(模型诊断)

#DHARMa scaled residuals(标准化模拟残差)

#11v11:
```{r positive, include=TRUE}
plot_glm_11 <- simulateResiduals(GLM_11v11_1)
plot(plot_glm_11)
```


#7V7:
```{r positive, include=TRUE}
plot_glm_7 <- simulateResiduals(GLM_7v7_1)
plot(plot_glm_7)
```

# 3.4 Statistical inference（统计推断）

#check the summary of retained model
```{r positive, include=TRUE}
summary(GLM_11v11_1)

summary(GLM_7v7_1)
```
#Model inference 
```{r positive, include=TRUE}
drop1(GLM_11v11_1,test = "Chisq") 

drop1(GLM_7v7_1,test = "Chisq") 
```


# 3.5 Sensitivity analysis (敏感性分析)

```{r Sensitivity2, include=TRUE}
xtabs(~ Condition + Transition +Format + positive_xt, data = df_all)
```
#The frequency distribution of the original data showed an imbalanced pattern.
#Defence-to-attacking transition type has extremely small sample size (n<5) under some cells.
#To evaluate the robustness of the fitted models, 
#this transition type was removed(only for sensitivity analysis)
#原始数据的频数分布不均，defence-to-attacking的样本量极小 (n<5)，
#为了测试模型的鲁棒性，将该传球类型去除（仅用于敏感性分析）


```{r Sensitivity2, include=TRUE}
#11v11
sens_11v11 <- subset(
  df_11v11,
  !(Transition %in%
      c("Defensive->Attacking"
        )))

GLM_sens_11v11 <- glmer(
  positive_xt ~ Condition + Transition + score_state + (1 | match_id),
  data = sens_11v11, family = binomial)

#7v7
sens_7v7 <- subset(
  df_7v7,
  !(Transition %in%
      c("Defensive->Attacking" )))

GLM_sens_7v7 <- glmer(
  positive_xt ~ Condition + Transition + score_state + (1 | match_id),
  data = sens_7v7, family = binomial)

```        

```{r Sensitivity2, include=TRUE}
drop1(GLM_sens_11v11, test = "Chisq")
        
drop1(GLM_sens_7v7, test = "Chisq")
```
#4. Visualisation（分布可视化）

#figure A：box plot for xt_added (图A：xT_added箱线图)

```{r data process2ad, include=TRUE}
ggplot(df_all, 
       aes(x = xT_added, y = Transition, 
                fill = Condition,
                linetype = Condition))  +
  geom_boxplot(linewidth = 0.2,width = 0.9,
               position = position_dodge(width = 0.8),
               outlier.size = 1
               ) +
  
  facet_grid(Format ~ .) +
  
  scale_fill_grey(start = 0.85, end = 0.35) +
  scale_linetype_manual(
    values = c("Bio-banding" = "solid", "Chronological-age" = "dashed")
  ) +

  #draw a line on xT_added=0(添加xT_added=0的参考线)
  scale_x_continuous(trans = "pseudo_log") +
  geom_vline(xintercept = 0, 
             linetype = "dashed", colour = "grey50") +
  
  theme_bw()+
  labs(x ="xT_added" , y = "Pass Type",
    title = "Distribution of xT_added values by pass type"
  )

```


#figure B：Transition pattern(图B：传球结构图)

```{r data process2ad, include=TRUE}
transition_summary <- aggregate( 
  list(n = df_all$Transition), 
  by = list( Condition = df_all$Condition, 
      Transition = df_all$Transition, 
      Format = df_all$Format ), 
  FUN = length )

transition_summary <- transition_summary %>% 
group_by(Condition, Format) %>% 
mutate(pct = n / sum(n)) %>% 
ungroup()
```

```{r data process2ad, include=TRUE}
ggplot(
  transition_summary,
  aes(
    x = Transition,
    y = pct,
    colour = Condition,shape= Condition
  )) +
  
  scale_colour_manual(
  values = c(
    "Chronological-age" = "black",
    "Bio-banding" = "grey"
  ))+
  
geom_point(size = 2, alpha = 0.8,
           position = position_dodge(width = 0.4)) +
    scale_shape_manual(
      values = c(
      "Bio-banding" = 16,      
      "Chronological-age" = 17    
  ))+

geom_line(
  aes(group = Condition,linetype = Condition),
  linewidth = 0.8
)+
      scale_linetype_manual(
  values = c(
    "Bio-banding" = "solid",
    "Chronological-age" = "dashed"))+
  
  scale_x_discrete(
    labels = c(
      "Attacking->Attacking" = "Att→Att",
      "Attacking->Middle" = "Att→Mid",
      "Middle->Attacking" = "Mid→Att",
      "Middle->Middle" = "Mid→Mid",
      "Middle->Defensive" = "Mid→Def",
      "Defensive->Middle" = "Def→Mid",
      "Defensive->Defensive" = "Def→Def",
      "Defensive->Attacking" = "Def→Att"
    ))+
  
facet_grid(Format ~ .) +
  
  theme_bw()+
  
    labs(x = "Pass Type", y = "percentage",
    title = "Percentage of pass type in each condition"
  )
```

#5. Descriptive summary for pass success.
#(附件：传球成功的分布描述)
```{r descriptive data, include=TRUE}
summary_df <-filter(df_all,`Action Type` == "Pass") %>%
  group_by(Format, Condition) %>%
  summarise(
    Total = n(),
    Successful = sum(Outcome == "Successful"),    #统计总数
    Success_rate = mean(Outcome == "Successful"),# 百分比
    .groups = "drop"
  )
summary_df
```
